\documentclass[14pt]{article}
\usepackage{extsizes}
\usepackage{import}
\usepackage{imakeidx}
\usepackage[utf8]{inputenc}
\usepackage{hyperref}
\usepackage{xcolor}
\usepackage{subfiles}
\import{}{fonts.tex}
\typeout{Requires XeLaTeX}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% License
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Original authors: Alec Markarian and 
% Benjamin Stanley
% LaTeX version author: André Santos
%
% URL to original work:
% https://forum.unity.com/threads/game-design-document-template.240038/
%
% This work is an adapted LaTeX version of the
% original document made by Alec Markarian and 
% Benjamin Stanley. This notice should not be
% removed, neither should the grey credits.
% The credits on this document should also remain 
% at exactly where they currently are (at the
% cover). The color, typography and size can
% be changed but should remain easily readable.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Custom Fonts
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% If you do not wish to use a custom font
% you can remove the fonts.tex file and its
% import command. 
% If you do intend on using custom fonts,
% you need to compile this project using
% XeLaTeX

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Hyperref link colors
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\hypersetup{
    colorlinks,
    citecolor=black,
    filecolor=black,
    linkcolor=darkgray,
    urlcolor=black
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Document title, author and date
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\title{<Your Game Name Here>}
\author{Author Name}
\date{Date Here}

\begin{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Colors
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\definecolor{notecolor}{rgb}{0.289, 0.21, 0}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Document Cover
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\clearpage
\maketitle
\thispagestyle{empty}
\vspace{8cm}

% CREDITS, DO NOT REMOVE!
% Original Work: 
\begin{center}
    \textcolor{gray}{\large This document is based on the GDD Template Written by: Alec Markarian and Benjamin Stanley}
\end{center}
\pagebreak

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Table of Contents
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Don't show page number on index
\thispagestyle{empty}
\tableofcontents
\thispagestyle{empty}
\pagebreak

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Document
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Overview}
\subsection{Theme / Setting / Genre}
\subsubsection{Theme}
<insert game theme here>

\subsubsection{Setting}
<insert game setting here>

\subsubsection{Genre}
<insert game genre here>

\section{Core Gameplay Mechanics Brief}
\begin{itemize}
    \item <Gameplay Mechanic \#1>
    \item <Gameplay Mechanic \#2>
    \item <Gameplay Mechanic \#3>  
    \item <Gameplay Mechanic \#4>
\end{itemize}

\subsection{Targeted Platforms}
\begin{itemize}
    \item <Example Platform \#1 Here>
    \item <Example Platform \#2 Here>
    \item <Example Platform \#3 Here>
\end{itemize}

\subsection{Monetization model (Brief/Document)}
<Monetization Type> (Premium, Paid Alpha/Beta/Final, Ad Driven, Micro-transactions, Subscription, etc.) \\
<Link to Monetization Document> 
(How do you plan to monetize the game?)

\subsection{Project Scope}
\subsubsection{Game Time Scale}
Time Scale (How long will it take to make this game?)

\subsubsection{Team Size}
<Core Team> \\
\hspace{1mm}		- Team Member name? \\
			- What does he/she do? \\
			- <Cost to employ them full time or part time> \\
		- etc. \\
- <Marketing Team> \\
		- Team Member name? \\ 
			- What does he/she do? \\
			- <Cost to employ them full time or part time> \\
		- Etc.
(List as many marketing team members as you need to)

\subsubsection{Projected Cost}
\subsubsection{Projected Time to Make}
\subsubsection{Team}
\subsubsection{Marketing Team}
\subsubsection{Licenses / Hardware / Other Costs}
\subsubsection{Total Cost Breakdown}

\subsection{Influences (Brief)}
\subsubsection{Influence \# 1}
- <Medium> (Television, Games, Literature, Movies, etc.)
- /Explain why this is an influence in 1 Paragraph or less/

\subsubsection{Influence \# 2}
- <Medium> (Television, Games, Literature, Movies, etc.)
- /Explain why this is an influence in 1 Paragraph or less/

\subsubsection{Influence \# 3}
- <Medium> (Television, Games, Literature, Movies, etc.)
- /Explain why this is an influence in 1 Paragraph or less/


\subsection{The elevator Pitch}
<A one sentence pitch for your game.> 
Pretend that your were pitching your game to a executive going to the elevator. You have less than 60 Seconds

\subsection{Brief Project Description}
<Two Paragraphs at least>
<No more than three paragraphs>
\pagebreak


\section{Detailed Project Description}
<Four Paragraphs or more If needs be>
<No more than six paragraphs>
\pagebreak


\section{What sets this project apart?}
\begin{itemize}
    \item <Reason \#1>
	\item <Reason \#2>
	\item <Reason \#3>
	\item <Reason \#4>
	\item <etc.>
\end{itemize}

\subsection{Core Gameplay Mechanics (Detailed)}
\subsubsection{Core Gameplay Mechanic \#1}
- <Details> \\
    Describe in 2 Paragraphs or less \\
- <How it works> \\
    Describe in 2 Paragraphs or less

\subsubsection{Core Gameplay Mechanic \#2}
- <Details> \\
    Describe in 2 Paragraphs or less \\
- <How it works> \\
    Describe in 2 Paragraphs or less   

\pagebreak
\section{Story and Gameplay}
\subsection{Story (Brief)}
<The Summary or TL;DR version of below>

\subsection{Story (Detailed)}
<Go into as much detail as needs be> \\
<Spare no detail> \\
<Use Mind Mapping software to get your point across>

\subsection{Gameplay (Brief)}
<The Summary version of below>

\subsection{Gameplay (Detailed)}
<Go into as much detail as needs be> \\
<Spare no detail> \\
<Combine this with the game mechanics section above>


\pagebreak
\section{Assets Needed}
\subsection{2D}
\subsubsection{Textures}
- Environment Textures

\subsubsection{Heightmap Data (If applicable)}
- List required data required - Example: DEM data of the entire UK

\subsubsection{Etc.}

\subsection{3D}
\subsubsection{Characters List}
\begin{itemize}
    \item Character \#1
    \item Character \#2
    \item Character \#3
    \item etc.
\end{itemize}

\subsubsection{Environmental Art Lists}
\begin{itemize}
    \item Example \#1
    \item Example \#2
    \item Example \#3
    \item etc.
\end{itemize}

\subsection{Sound}
\subsubsection{Sound List (Ambient)}
\paragraph{Outside}
\begin{itemize}
    \item Level 1
    \item Level 2
    \item Level 3
    \item etc.
\end{itemize}

\paragraph{Inside}
\begin{itemize}
    \item Level 1
    \item Level 2
    \item Level 3
    \item etc.
\end{itemize}

\subsubsection{Sound List (Player)}
\paragraph{Character Movment Sound List}
\begin{itemize}
    \item Example 1
    \item Example 2
    \item etc.
\end{itemize}

\paragraph{Character Hit / Collision Sound list}
\begin{itemize}
    \item Example 1
    \item Example 2
    \item etc.
\end{itemize}

\paragraph{Character on Injured / Death sound list}
\begin{itemize}
    \item Example 1
    \item Example 2
    \item etc.
\end{itemize}

\subsection{Code}
\subsubsection{Character Scripts (Player Pawn/Player Controller)}

\subsubsection{Ambient Scripts (Runs in the background)}
\begin{itemize}
    \item Example
    \item etc.
\end{itemize}

\subsubsection{NPC Scripts}
\begin{itemize}
    \item Example
    \item etc.
\end{itemize}

\subsection{Animation}
\subsubsection{Environment Animations}
\begin{itemize}
    \item Example
    \item etc.
\end{itemize}

\subsubsection{Character Animations}
\paragraph{Player}
\begin{itemize}
    \item Example
    \item etc.
\end{itemize}

\paragraph{NPC}
\begin{itemize}
    \item Example
    \item etc.
\end{itemize}

\pagebreak
\section{Schedule}
\subsection{Object \#1}
\begin{itemize}
    \item Milestone 1
    \item Milestone 2
    \item etc.
\end{itemize}

\subsection{Object \#22}
\begin{itemize}
    \item Milestone 1
    \item Milestone 2
    \item etc.
\end{itemize}

\end{document}
